Miniproject - Algebraic Geometry

### 2021-12-10 Algebraic geometry/submission.tex
changed layout of alg geo

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{example}[definition]{Example}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{theorem}[definition]{Theorem}

@@

\begin{lemma}[1a]
    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
\end{lemma}
\begin{proof}
    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
    \begin{align*}
        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) - \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
        =& \begin{cases}
            \beta v_1 + \gamma v_2 \wedge \frac \alpha \beta v_2 + v_3 & \text{if $\beta \neq 0$} \\
            \alpha v_1 - \gamma v_3 \wedge v_2 & \text{otherwise}
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
    \end{align*}
    are decomposable.
    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
\end{proof}

\begin{example}[1b]
    Consider $V = k^4$. 
    Then the element $w := (e_1 \wedge e_2) + (e_3 \wedge e_4) \in \extpow^2(V)$ is not decomposable. 
\end{example}
\begin{proof}
    Assume it was, then there are $a, b \in k^4$ such that
    \begin{equation*}
        w = \sum_i a_i e_i \wedge \sum_j b_j e_j = \sum_{i < j} (a_i b_j - a_j b_i) (e_i \wedge e_j)
    \end{equation*}
    In other words
    \begin{equation*}
        a_1b_2 - a_2b_1 = 1, \ a_3b_4 - a_4b_3 = 1, \ a_i b_j - a_j b_i = 0 \ \text{for all $(i, j) \neq (1, 2), (3, 4)$}
    \end{equation*}
    Clearly $a_1 b_2 \neq 0$ or $a_2 b_1 \neq 0$.
    Similarly, have $a_3 b_4 \neq 0$ or $a_4 b_3 \neq 0$.
    As all expressions are symmetric w.r.t swapping $a_1, b_2$ with $a_2, b_1$ and $a_3, b_4$ with $a_4, b_3$, we may assume wlog that $a_1 b_2, a_3 b_4 \neq 0$.

@@

\begin{lemma}[1c]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

@@

In this part, we want to consider the connection of external powers to the Grassmanian.
First of all, assume there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$. 
Then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
\begin{equation*}
    u_i = \sum_j a_{ij} v_j
\end{equation*}
So by Lemma~\ref{prop:linear_transform_extpow}, it follows that
\begin{equation*}
    u_1 \wedge ... \wedge u_d = \det(A) (v_1 \wedge ... \wedge v_d)
\end{equation*}
As $v_1, ..., v_d$ resp. $u_1, ..., u_d$ are bases, they are linearly independent and in particular, we see that
\begin{equation*}
    v_1 \wedge ... \wedge v_d \neq 0 \quad \text{and} \quad u_1 \wedge ... \wedge u_d \neq 0
\end{equation*}
by Lemma~\ref{prop:extpow_zero_iff_independent}.
Hence they have well-defined images $[v_1 \wedge ... \wedge v_d]$ resp. $[u_1 \wedge ... \wedge u_d]$ in the projective space $\Proj(\extpow^d V)$.
By the above, find
\begin{equation*}
    [v_1 \wedge ... \wedge v_d] = [u_1 \wedge ... \wedge u_d]
\end{equation*}
This allows us to study the Grassmanian $\Gr(d, V)$ of a fixed vector space $V$.
\begin{definition}
    Define the map
    \begin{equation*}
        \phi: \Gr(d, V) \to \Proj(\extpow^d V), \quad \vspan\{v_1, ..., v_d\} \mapsto [v_1 \wedge ... \wedge v_d]
    \end{equation*}
    which is well-defined by Lemma~\ref{prop:linear_transform_extpow} as described above.
\end{definition}
\begin{lemma}[1a]
    We have
    \begin{equation*}
        \mathrm{im}\phi = D := \{ [v] \in \Proj(\extpow^d V) \ | \ \text{$v$ decomposable}\}
    \end{equation*}
\end{lemma}
\begin{proof}
    First of all, note that the set $D$ is well-defined, as $v$ is decomposable if and only if $\lambda v$ is decomposable, for all $\lambda \in k^*$.

@@

    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[2b]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = \bar{f} \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[2c]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}

@@

\begin{proposition}[3a]

@@

\begin{example}[2b]

@@

\begin{example}[2c]

@@

    Now we know that $C(I)$ is an independent set with $\sum_{\alpha \in C(I)} l(\alpha) < \sum_{\alpha \in I} l(\alpha)$.
    Since these sums take values in $\N$ which is well-ordered, we cannot have an infinite sequence
    \begin{equation*}
        I, C(I), C^2(I), C^3(I), ...
    \end{equation*}
    and thus at some point, we find $C^k(I)$ is contained in layer 0.
    Now note that $C$ does not decrease the size, i.e. $|C(I)| = |I|$ and so $|C^k(I)| = |I|$.
    However, there are only $(n - 2) + (n - 2) + 1 = 2n - 3$ elements in layer 0 and the claim follows.
\end{proof}
\begin{corollary}
    Have $\dim(\Gr(2, n)) = 2n - 4$.
\end{corollary}
\begin{proof}
    Follows directly from the previous two statements.
\end{proof}
I also think that it is not too difficult to show that
\begin{equation*}
    s_n(2n - 3) = \frac {(2(n - 2))!} {(n - 2)! (n - 1)!}
\end{equation*}
which then shows the degree formula for the case $d = 2$.
However, this is not a lecture on graph theory or combinatorics, and I already spent a lot of hours on this problem (and there are other mini projects as well :)).
So I will not do the proof here, but I think it is already very interesting to see those graphs and the connection of $\deg(\Gr(2, n))$ to combinatorial problems.
Finally, in the case of $n = 6$ we can simply count the independent sets by hand, and find the following result.
\begin{corollary}
    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 15$.
\end{corollary}
\begin{proof}
    The dimension follows directly from the previous general case.
    For the degree, just count the maximal independent sets in $G_6$, as displayed in Example~\ref{ex:Gn}.
    This is slightly tricky, but it is not too hard to see that there are exactly 15 of them.
\end{proof}
Of course, the above statement on $\Gr(2, 6)$ can also easily be found using Computer Algebra.
For example, the following Sage script shows that
\begin{equation*}
    p_{\Gr(2, 6)} = \frac 1 {2880} t^8 + \frac 1 {120} t^7 + \frac {41} {480} t^6 + \frac {39} {80} t^5 + \frac {541} {320} t^4 + \frac {291} {80} t^3 + \frac {3401} {720} t^2 + \frac {101} {30} t + 1
\end{equation*}
from which we easily deduce that
\begin{equation*}
    \dim(\Gr(2, 6)) = 8 \quad \text{and} \quad \deg(\Gr(2, 6)) = \frac 1 {2880} \cdot 8! = 14
\end{equation*}
\lstinputlisting[language = python]{./gr26.sage}
\printbibliography
\end{document}

>>>>

\theoremstyle{definition}
\newtheorem{definition}[subsection]{Definition}
\newtheorem{remark}[subsection]{Remark}
\newtheorem{lemma}[subsection]{Lemma}
\newtheorem{example}[subsection]{Example}
\newtheorem{proposition}[subsection]{Proposition}
\newtheorem{corollary}[subsection]{Corollary}
\newtheorem{theorem}[subsection]{Theorem}

@@

\begin{lemma}[Question (a)]
    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
\end{lemma}
\begin{proof}
    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
    \begin{align*}
        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) - \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
        =& \begin{cases}
            \beta v_1 + \gamma v_2 \wedge \frac \alpha \beta v_2 + v_3 & \text{if $\beta \neq 0$} \\
            \alpha v_1 - \gamma v_3 \wedge v_2 & \text{otherwise}
        \end{cases}
    \end{align*}
    and
    \begin{align*}
        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
    \end{align*}
    are decomposable.
    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
\end{proof}

\begin{example}[Question (b)]
    Consider $V = k^4$. 
    Then the element $w := (e_1 \wedge e_2) + (e_3 \wedge e_4) \in \extpow^2(V)$ is not decomposable. 
\end{example}
\begin{proof}
    Assume it was, then there are $a, b \in k^4$ such that
    \begin{equation*}
        w = \sum_i a_i e_i \wedge \sum_j b_j e_j = \sum_{i < j} (a_i b_j - a_j b_i) (e_i \wedge e_j)
    \end{equation*}
    In other words
    \begin{equation*}
        a_1b_2 - a_2b_1 = 1, \ a_3b_4 - a_4b_3 = 1, \ a_i b_j - a_j b_i = 0 \ \text{for all $(i, j) \neq (1, 2), (3, 4)$}
    \end{equation*}
    Clearly $a_1 b_2 \neq 0$ or $a_2 b_1 \neq 0$.
    Similarly, have $a_3 b_4 \neq 0$ or $a_4 b_3 \neq 0$.
    As all expressions are symmetric w.r.t swapping $a_1, b_2$ with $a_2, b_1$ and $a_3, b_4$ with $a_4, b_3$, we may assume wlog that $a_1 b_2, a_3 b_4 \neq 0$.

@@

\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

@@

In this part, we want to consider the connection of external powers to the Grassmanian.
\begin{remark}[Question (a)]
    First of all, assume there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$. 
    Then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
    \begin{equation*}
        u_i = \sum_j a_{ij} v_j
    \end{equation*}
    So by Lemma~\ref{prop:linear_transform_extpow}, it follows that
    \begin{equation*}
        u_1 \wedge ... \wedge u_d = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    As $v_1, ..., v_d$ resp. $u_1, ..., u_d$ are bases, they are linearly independent and in particular, we see that
    \begin{equation*}
        v_1 \wedge ... \wedge v_d \neq 0 \quad \text{and} \quad u_1 \wedge ... \wedge u_d \neq 0
    \end{equation*}
    by Lemma~\ref{prop:extpow_zero_iff_independent}.
    Hence they have well-defined images $[v_1 \wedge ... \wedge v_d]$ resp. $[u_1 \wedge ... \wedge u_d]$ in the projective space $\Proj(\extpow^d V)$.
    By the above, find
    \begin{equation*}
        [v_1 \wedge ... \wedge v_d] = [u_1 \wedge ... \wedge u_d]
    \end{equation*}
\end{remark}
This allows us to study the Grassmanian $\Gr(d, V)$ of a fixed vector space $V$.
\begin{definition}
    Define the map
    \begin{equation*}
        \phi: \Gr(d, V) \to \Proj(\extpow^d V), \quad \vspan\{v_1, ..., v_d\} \mapsto [v_1 \wedge ... \wedge v_d]
    \end{equation*}
    which is well-defined by Lemma~\ref{prop:linear_transform_extpow} as described above.
\end{definition}
\begin{lemma}[1a]
    We have
    \begin{equation*}
        \mathrm{im}\phi = D := \{ [v] \in \Proj(\extpow^d V) \ | \ \text{$v$ decomposable}\}
    \end{equation*}
\end{lemma}
\begin{proof}
    First of all, note that the set $D$ is well-defined, as $v$ is decomposable if and only if $\lambda v$ is decomposable, for all $\lambda \in k^*$.

@@

    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[Question (b)]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = \bar{f} \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[Question (c)]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}

@@

\begin{proposition}[Question (a)]

@@

\begin{example}[Question (b)]

@@

\begin{example}[Question (c), (d)]

@@

    Now we know that $C(I)$ is an independent set with $\sum_{\alpha \in C(I)} l(\alpha) < \sum_{\alpha \in I} l(\alpha)$.
    Since these sums take values in $\N$ which is well-ordered, we cannot have an infinite sequence
    \begin{equation*}
        I, C(I), C^2(I), C^3(I), ...
    \end{equation*}
    and thus at some point, we find $C^k(I)$ is contained in layer 0.
    Now note that $C$ does not decrease the size, i.e. $|C(I)| = |I|$ and so $|C^k(I)| = |I|$.
    However, there are only $(n - 2) + (n - 2) + 1 = 2n - 3$ elements in layer 0 and the claim follows.
\end{proof}
\begin{corollary}
    Have $\dim(\Gr(2, n)) = 2n - 4$.
\end{corollary}
\begin{proof}
    Follows directly from the previous two statements.
\end{proof}
I also think that it is not too difficult to show that
\begin{equation*}
    s_n(2n - 3) = \frac {(2(n - 2))!} {(n - 2)! (n - 1)!}
\end{equation*}
which then shows the degree formula for the case $d = 2$.
However, this is not a lecture on graph theory or combinatorics, and I already spent a lot of hours on this problem (and there are other mini projects as well :)).
So I will not do the proof here, but I think it is already very interesting to see those graphs and the connection of $\deg(\Gr(2, n))$ to combinatorial problems.
Finally, in the case of $n = 6$ we can simply count the independent sets by hand, and find the following result.
\begin{corollary}[Question (e)]
    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 15$.
\end{corollary}
\begin{proof}
    The dimension follows directly from the previous general case.
    For the degree, just count the maximal independent sets in $G_6$, as displayed in Example~\ref{ex:Gn}.
    This is slightly tricky, but it is not too hard to see that there are exactly 15 of them.
\end{proof}
Of course, the above statement on $\Gr(2, 6)$ can also easily be found using Computer Algebra.
For example, the following Sage script shows that
\begin{equation*}
    p_{\Gr(2, 6)} = \frac 1 {2880} t^8 + \frac 1 {120} t^7 + \frac {41} {480} t^6 + \frac {39} {80} t^5 + \frac {541} {320} t^4 + \frac {291} {80} t^3 + \frac {3401} {720} t^2 + \frac {101} {30} t + 1
\end{equation*}
from which we easily deduce that
\begin{equation*}
    \dim(\Gr(2, 6)) = 8 \quad \text{and} \quad \deg(\Gr(2, 6)) = \frac 1 {2880} \cdot 8! = 14
\end{equation*}
\lstinputlisting[language = python]{./gr26.sage}
\printbibliography
\end{document}
